First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
stepans 4th comments

\newcommand*{\ANL}{Argonne National Laboratory, Argonne, Illinois 60439}
\newcommand*{\ANLindex}{1}
\affiliation{\ANL}
\newcommand*{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\newcommand*{\ORSAYindex}{2}
\affiliation{\ORSAY}
\newcommand*{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\JLABindex}{3}
\affiliation{\JLAB}

@@

\author {M.~Hattawy}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {N.A.~Baltzell} 
\affiliation{\ANL}
\affiliation{\JLAB}
\author {R.~Dupr\'{e}} 
\email[corresponding author: ]{dupre@ipno.in2p3.fr}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {K.~Hafidi} 
\affiliation{\ANL}
\author{S.~Stepanyan}
\affiliation{\JLAB}

@@

The DVCS and well-known Bethe-Heitler (BH) processes, where the real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of real photon 
electroproduction is a sum of the amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, while the DVCS amplitude is 
a combination of the form factors and GPDs. At our kinematics, the cross 
section of real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. Its effect is however
enhanced in the observables sensitive to the interference term, {\it e.g.} 
beam spin asymmetry. The three terms entering the cross section calculation, the 
BH and DVCS amplitudes squared and their interference term, 
can be expressed by a finite sum of Fourier harmonics, as shown for the nucleon 
in \cite{Belitsky:2001ns} and for the spin-zero targets in 
\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
asymmetry ($A_{LU}$) of a spin-zero hadron can be expressed as:
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depends on the GPD 
$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors $\alpha_i$
depend on azimuthal angle $\phi$, the nuclear form factor 
$F_A(t)$, $Q^2$ and $x_B$. These factors are expressed as:
\begin{align}
   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
   \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
      {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
      \epsilon^2},
\end{align}
where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
in the leptonic tensor.  The explicit expressions of these terms can be found 
in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

In this work the azimuthal dependence of the BSA, $A_{LU}$, has been studied 
for a wide range of kinematics. We identified two main backgrounds to our 
measurement, accidental coincidences and exclusive coherent $\pi^0$ production.  
The accidentals have particles originating from different events, and we 
estimate their  contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with an electron and 
helium originating from different vertices. Regarding the $\pi^0$ production, 
it can easily be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the importance of this background, we developed an event generator 
calibrated on the experimental yield of exclusive $\pi^0$ measured by our 
experiment. We used this generator together with a GEANT3 simulation of our 
detector to estimate the ratio between the number of $\pi^0$ events where the 
two photons are detected and those that is misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data.  Depending on the kinematics, we found contaminations of 
2 to 4\%. The study of systematic uncertainties showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%). However, added quadratically,the total systematic 
uncertainty is about 10\%, which is significantly smaller than statistical 
uncertainties in all kinematical bins.

>>>>

\newcommand*{\ANL}{Argonne National Laboratory, Argonne, Illinois 60439}
\newcommand*{\ANLindex}{1}
\affiliation{\ANL}
\newcommand*{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\newcommand*{\ORSAYindex}{2}
\affiliation{\ORSAY}
\newcommand*{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\JLABindex}{3}
\affiliation{\JLAB}
\newcommand*{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
\newcommand*{\ODUindex}{4}
\newcommand*{\INFNGE}{INFN, Sezione di Genova, 16146 Genova, Italy}
\newcommand*{\INFNGEindex}{5}
\newcommand*{\UTFSM}{Universidad T\'{e}cnica Federico Santa Mar\'{i}a, Casilla 110-V Valpara\'{i}so, Chile}
\newcommand*{\UTFSMindex}{6}
\newcommand*{\MISS}{Mississippi State University, Mississippi State, MS 39762-5167}
\newcommand*{\MISSindex}{7}
\newcommand*{\VIRGINIA}{University of Virginia, Charlottesville, Virginia 22901}
\newcommand*{\VIRGINIAindex}{8}

@@

\author {M.~Hattawy}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {N.A.~Baltzell} 
\affiliation{\ANL}
\affiliation{\JLAB}
\author {R.~Dupr\'{e}} 
\email[corresponding author: ]{dupre@ipno.in2p3.fr}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {K.~Hafidi} 
\affiliation{\ANL}
\author{S.~Stepanyan}
\affiliation{\JLAB}
\author {S.~Bultmann} 
\affiliation{\ODU}
\author{R.~De~Vita} 
\affiliation{\INFNGE}
\author {A.~El~Alaoui} 
\affiliation{\ANL}
\affiliation{\UTFSM}
\author {L.~El~Fassi} 
\affiliation{\MISS}
\author{H.~Egiyan}
\affiliation{\JLAB}
\author{F.X.~Girod} 
\affiliation{\JLAB}
\author{S.~Liuti} 
\affiliation{\VIRGINIA}
\author {B.~Torayev} 
\affiliation{\ODU}
\author {E.~Voutier} 
\affiliation{\ORSAY}

@@

The DVCS and well-known Bethe-Heitler (BH) processes, where the real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of real photon 
electroproduction is a sum of the amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, while the DVCS amplitude is 
a combination of the form factors and GPDs. At our kinematics, the cross 
section of real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. Its effect is however
enhanced in the observables sensitive to the interference term, {\it e.g.} 
beam spin asymmetry. The three terms entering the cross section calculation,
the BH and DVCS amplitudes squared and their interference term, 
can be decomposed into a finite sum of Fourier harmonics in the azimuthal angle
$\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
shown for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets
in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
asymmetry ($A_{LU}$) of a spin-zero hadron can be expressed as:
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depends on the GPD 
$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors $\alpha_i$
depend on azimuthal angle $\phi$, the nuclear form factor 
$F_A(t)$, $Q^2$ and $x_B$. These factors are written as:
\begin{align}
   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
   \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
      {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
      \epsilon^2},
\end{align}
where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
in the leptonic tensor.  The explicit expressions of these terms can be found 
in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

In this work the azimuthal dependence of the BSA, $A_{LU}$, has been studied 
for a wide range of kinematics. We identified two main backgrounds to our 
measurement, accidental coincidences and exclusive coherent $\pi^0$ production.  
The accidentals have particles originating from different events, and we 
estimate their  contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with an electron and 
helium originating from different vertices. Regarding the $\pi^0$ production, 
it can easily be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the importance of this background, we developed an event generator 
tuned on the experimental yield of exclusive $\pi^0$ measured by our 
experiment. We used this generator together with a GEANT3 simulation of our 
detector to estimate the ratio between the number of $\pi^0$ events where the 
two photons are detected and those that is misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data.  Depending on the kinematics, we found contaminations of 
2 to 4\%. The study of systematic uncertainties showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%). However, added quadratically,the total systematic 
uncertainty is about 10\%, which is significantly smaller than statistical 
uncertainties in all kinematical bins.
